\subsubsection{LLP parsing}
The idea of the $\LLP(q, k)$ grammar class comes from wanting to create a $\LL(k)$ like grammar class, which can be parsed in parallel. To do this a definition for a LLP configuration will be needed.
\begin{definition}[LLP parser configuration]
    \label{def:llp-configuration}
    Let $G = (N, T, P, S)$ be a context-free grammar that is a $\LLP(q, k)$ grammar for some $q, k \in \mathbb{Z}_+$. Let $(x, y)$ be a pair such that $xy$ occurs as a substring in $\mathcal{L}(G)$\footnote{This is the set of all derivable strings ${s \in T^* : S \Rightarrow^* s}$ here $\Rightarrow^*$ is almost the same relation as $\Rightarrow$ but transitive and reflexive.}, $x \in T^{*q}$\footnote{This set is defined to be $\{t \in T^* : |t| \leq q\}$.}, $y \in T^{*k}$. If $\PSLS(x,y) = \{\omega\}$ the pair $(x, y)$ has the following LLP configuration.
    \begin{align*}
        (\omega, \alpha, \pi) \in (T \cup N)^* \times (T \cup N)^* \times \mathcal{S}
    \end{align*}
    Where $\omega$ is the initial pushdown store, $\alpha$ is the final pushdown store after parsing $(y, \omega, (\;)) = (vw, \omega, (\;)) \vdash^* (w, \alpha, \pi)$, $v \in T$, $w \in T^*$ and $\pi$ are the resulting productions.
\end{definition}
\noindent The idea now is, that you would start off by creating every pair $\mathcal{P}$ that can occur in the given input string. These pairs are defined to be the following.
\begin{align*}
    \mathcal{P} =&\; \{((x, y), i) : w = \delta xy_i \beta, |x| = q, |y_i| = k\} \\
    \cup&\; \{((x, y), i) : w = xy_i \beta, |x| \leq q, |y| = k\} \\
    \cup&\; \{((x, y), i) : w = \delta xy_i, |x| = q, |y| \leq k\}
\end{align*}
Where $i \in \mathbb{N}$ denotes the index of where the start of the substring $y_i$ starts, this $i$ is used such that the ordering can be kept. Then we would want to create a table look up function $\Phi: T^* \times T^* \to (T \cup N)^* \times (T \cup N)^* \times \mathcal{S}$. This function maps the pairs $(x,y)$ to a triplet $(\omega, \alpha, \pi)$ which is much the same as the configuration described in definition \ref{def:ll-configuration}. 

After all the $x, y$ pairs have been constructed $\Phi$ is mapped over all the pairs. The idea is now to check if the configuration besides each other $((\omega, \alpha, \pi), i)$ and $((\bar{\omega}, \bar{\alpha}, \bar{\pi}), i + 1)$ matches on $\alpha$ and $\bar{\omega}$. This can be done using the associative $\mathbf{glue}$ binary operation, which is described in detail in the LLP paper \cite[7]{Vagner2007} or using Algorithm 18 \cite[18]{Vagner2007}. Using $\mathbf{glue}$ you can do a parallel reduce since it is associative.

This description will suffice for the theory needed to explain the important parts of the LLP paper \cite{Vagner2007} in relation to this paper.

\subsubsection{The PSLS definition}
To construct $\Phi$ function Algorithm 8, 9 and 13 \cite[13, 15]{Vagner2007} can be used where Algorithm 13 results in the final table which is $\Phi$. There is just the problem that Algorithm 8 contains a mistake. This is due to Definition 6 \cite[12]{Vagner2007} which is the definition of the PSLS function.

The function $\PSLS: T^* \times T^* \to \mathbb{P}((N \cup T)^*)$ is a function that finds the Prefix of a Suffix of a Leftmost Sentential form. This function is able to determine the initial pushdown store $\omega$ in an LLP configuration $(\omega, \alpha, \pi)$ for the pair $(x, y)$.

The trouble occurs when considering the following $\LL(2)$ grammar.
Let $G = (S', \{\vdash, \dashv, a\} \{S', S, A\}, P)$ be an augmented grammar where $P$ is a set of the following productions. 
\begin{align*}
    0)\:\: S' \to \: \vdash S \dashv \qquad 1)\:\: A \to \varepsilon \qquad 2)\:\: S \to aAa \qquad 3)\:\: A \to a
\end{align*}
The augmentation comes from Algorithm 8 \cite[13]{Vagner2007} and introduces production 0. If you now were to use the definition from the paper as it is you would arrive at the following PSLS table.
\begin{table}[H]
    \centering
    \begin{tabular}{c|c|c|c}
        & $\dashv$ & $a\dashv$ & $aa$ \\ \hline
        $\vdash$ & & & $\{S\}$ \\\hline
        $\vdash a$ & & $\{A\}$ & $\{A\}$ \\\hline
        $aa$ & $\dashv$ & $\{a\}$ & 
    \end{tabular}
    \caption{The computed PSLS table using Algorithm 8 \cite[13]{Vagner2007}.}
\end{table}
\noindent To construct the table function that maps admissible pairs to LLP configurations, Algorithm 13 \cite[15]{Vagner2007} will be needed. This Algorithm needs a $\LL(k)$ parser so the following $\LL(2)$ table is constructed.
\begin{table}[H]
    \centering
    \begin{tabular}{c|c|c|c}
        & $\vdash a$ & $aa$ & $a\dashv$ \\ \hline
        $S'$ & $S' \to \: \vdash S \dashv$ & & \\\hline
        $S$ & & $S \to aAa$ & \\\hline
        $A$ & & $A \to a$ & $A \to \varepsilon$
    \end{tabular}
    \caption{The $\LL(2)$ parsing table.}
\end{table}
\noindent The trouble you run into is if you create the LLP configuration from the $\PSLS$ table entry $(\vdash a,a \dashv)$. Then Algorithm 13 states that you need to parse the first symbol of the lookahead string $a \dashv$ to obtain the final pushdown store and the production sequence. But when you try to parse $(a \dashv, A, ())$ then you get $(a \dashv, A, ()) \vdash (a \dashv, \varepsilon, 1)$ due to the parser table. Because of this you would never be able to parse the first symbol and Algorithm 13 would fail.

This can be fixed by changing the PSLS definition such that it is dependent on $k$, it could then be called $\PSLS_k$ instead. The dependency would result in $\FIRST_k$ being used instead of $\FIRST_1$\footnote{There are also some other changes made besides this which are mentioned in section \ref{sec:assumptions}.}.
\begin{definition}[$\PSLS_k$]
    Let $G = (N, T, P, S)$ be a context-free grammar. The function $\PSLS_k(x, y)$ for a pair of strings $x, y \in T^*$ is defined as follows:\footnote{$\Rightarrow_{lm}^*$ is much the same as $\Rightarrow^*$ but only leftmost derivable strings are considered in the relation.}
    \begin{align*}
        \PSLS_k(x, y) = \{ & \alpha : \exists S \Rightarrow^*_{lm} wuA\beta \Rightarrow wxB\gamma \Rightarrow^* wxy\delta, \\
        & w, u \in T^*, A, B \in N, \alpha, \beta, \gamma, \delta \in (N \cup T)^*, u \neq x, \\
        & \alpha \text{ is the shortest prefix of } B\gamma \text{ such that } y \in \FIRST_k(\alpha) \} \\
        \cup \: \{ & y : \exists S \Rightarrow^* wuA\beta \Rightarrow wxa\gamma \Rightarrow wxy\delta, \\
        & a = \FIRST_1(y), w,u \in T^*, \beta, \gamma, \delta \in (N \cup T)^*, u \neq x \}
    \end{align*}
\end{definition}
\noindent And Algorithm 8 would then be changed when solving for the shortest prefix.
\begin{algorithm}[Construction of a collection of sets of $\LLP(q, k)$ items.]
    Input: A context-free grammar $G = (N, T, P, S)$ that is $\LL(k)$. Ouput: A collection $C$ of sets of $\LLP(q, k)$ items for $G$.
    \begin{enumerate}
        \item The grammar is augmented in the following way:
        \begin{align*}
            G' = (N', T', P', S') = (N \cup \{S'\}, T \cup \{\vdash, \dashv\}, P \cup \{S' \to \vdash S \dashv\}, S')
        \end{align*}
        where $S'$ is a new nonterminal symbol and $\vdash, \dashv$ are new terminal symbols.
        \item The initial set of $\LLP(q, k)$ items is constructed as follows:
        \begin{enumerate}
            \item $D_0 := \{[S' \to \: \vdash S \dashv \bigdot, u, \varepsilon, \varepsilon] : u \in \LAST_q(\vdash S \dashv) \}$
            \item $C := \{D_0\}$
        \end{enumerate}
        \item If a set of $\LLP(q, k)$ items has been constructed, then a new set $D_j$ is constructed
        for each symbol $X \in N' \cup T'$ standing just before the dot in $D_i$. The set $D_j$ is constructed as follows:
        \begin{enumerate}
            \item $D_j := \{[Y \to \alpha\bigdot X \beta, u_j, v_j, \gamma] : [Y \to aX\bigdot\beta, u_i, v_i, \delta] \in D_i, u_j \in \bigcup_{\omega \in \BEFORE_q(Y) \alpha} \LAST_q(\omega), v_j \in \FIRST_k(Xv_i), \gamma$ is the shortests prefix of $X\delta$ such that $v_j \in \FIRST_k(\gamma)\}$.
            \item If $[X \to \alpha Y\bigdot \beta, u, v,\gamma] \in D_j, Y \in N'$ and $Y \to \delta \in P'$, then $D_j := D_j \cup \{[Y \to \delta \bigdot , u', v, \gamma] : u' \in \bigcup_{\omega \in \BEFORE_q(Y) \delta} \LAST_q(\omega)\}$.
            \item Repeat step (3b) till no new item can be added into $D_j$.
            \item $C := C \cup \{D_j\}$
        \end{enumerate}
        \item Repeat step (3) for all created sets till no new set can be added into $C$.
    \end{enumerate}
\end{algorithm}
\noindent Using the new definition and algorithm would result in the following PSLS table.
\begin{table}[H]
    \centering
    \begin{tabular}{c|c|c|c}
        & $\dashv$ & $a\dashv$ & $aa$ \\ \hline
        $\vdash$ & & & $\{S\}$ \\\hline
        $\vdash a$ & & $\{Aa\dashv\}$ & $\{Aa\}$ \\\hline
        $aa$ & $\{\dashv\}$ & $\{a\dashv\}$ & 
    \end{tabular}
    \caption{The computed PSLS table using the new PSLS definition.}
\end{table}
\noindent Using the new definition to create the LLP configuration from $Aa\dashv$ which is the table $(\vdash a,a \dashv)$ would now succeed. This is due to $(a \dashv, Aa\dashv, ()) \vdash (a \dashv, a\dashv, 1) \vdash ( \dashv, \dashv, 1)$.

This changed definition would still work for $\LLP$ parsing. The difference is the prefix of a suffix of a sentential form found via $\PSLS$ is now guaranteed to be able to parse the first symbol. Since the pushdown store will always have enough symbols to derive the $k$ first symbols of the input.

It is important to note that this argument needs some assumptions. Before these assumptions will be accounted for a typo in Algorithm 13 \cite[15]{Vagner2007} will be cleared up. This typo is the pushdown store and input string is switched in the 3-tuple because of the definition in the LLP paper \cite[5]{Vagner2007}.

The assumption is that Algorithm 13 uses implicitly the lookahead in the LL configuration. This is assumed since only one symbol in the input string of the LL configuration appears. If the lookahead is not accounted for then $\LL(1)$ parsing would only be possible. This is a reasonable assumption since the paper says the following about their parallel LL parsing method.
\begin{center}
    ``The method is not universal because only a subset of $\LL(k)$ grammars can be deterministically parsed in this way.'' \cite[2]{Vagner2007}
\end{center}
If Algorithm 13 only used $\LL(1)$ then it would be true the method is a subset of $\LL(k)$. It would then have been more precise to write their method only works for a subset of $\LL(1)$. Therefore, it is assumed that $\LL(k)$ parsing is meant to be used in Algorithm 13. Because of this assumption the example shown here with the original PSLS definition will fail.

\subsubsection{Infinite loop}\label{sec:infinite_loop}
There is an infinite loop in Algorithm 8 \cite[13]{Vagner2007}. It will be shown in this section that the infinite loop can occur. Consider the following augmented grammar.
\begin{align*}
    S' \to \: \vdash S \dashv \quad S \to aSA \quad A \to \varepsilon \quad S \to b
\end{align*}
This grammar is $\LL(1)$, so you should be able to use Algorithm 8 to determine the $\PSLS$ table and therefore determine if it is $\LLP(1, 1)$. If you try to construct the LLP item collection for the given grammar with $q = 1$ and $k = 1$ what you find is.
\begin{align*}
    D_0 = \{& [S' \to \: \vdash S \dashv\bigdot, \dashv, \varepsilon, \varepsilon]\} \\
    D_1 = \{& [A \to \bigdot , b, \dashv, \dashv], [S \to a S A\bigdot , b, \dashv, \dashv], \\
    & [S \to b\bigdot , b, \dashv, \dashv],[S' \to \vdash S\bigdot \dashv, b, \dashv, \dashv]\} \\
    & \qquad\qquad\qquad\quad \vdots
\end{align*}
The problem will occur due to the tuple $[S \to a S A\bigdot , b, \dashv, \dashv]$. This item will become a singleton set when grouping the set $D_1$ in the start of step 3. In step 3 (a) you are able to create the tuple $[S \to a S\bigdot A, b, \dashv, A \dashv]$. This is due to:
\begin{align*}
    & b \in \bigcup_{\omega \in \BEFORE_1(S) aS} \LAST_1(\omega) = \bigcup_{\omega \in \{\vdash aS, aaS\}} \LAST_1(\omega) = \LAST_1(S) = \{b\} \\
    & \dashv \:\, \in \FIRST_1(A\dashv) \text{ since } A \Rightarrow^* \varepsilon \\
    & A\dashv \text{ is the shortests prefix of } A\dashv \text{ such that } \dashv \:\,\in \FIRST_1(A\dashv)
\end{align*}
Because $[S \to a S\bigdot A, b, \dashv, A \dashv]$ occurs, then the production $S \to a S A\bigdot$ also appears in some item in $D_j$ due to step 3 (b). This item has the same prefix and same shortest prefix as $[S \to a S\bigdot A, b, \dashv, A \dashv]$. The suffix $b$ will also appear in the next tuple because. 
\begin{align*}
    \bigcup_{\omega \in \BEFORE_1(S) aSA} \LAST_1(\omega) = \bigcup_{\omega \in \{\vdash aSA, aaSA\}} \LAST_1(\omega) = \LAST_1(S) = \{b\}
\end{align*}
Because of this $[S \to a SA\bigdot, b, \dashv, A \dashv]$ is a member of the new set $D_j$ which is:
\begin{align*}
    \{ &[A \to \bigdot , b, \dashv, A \dashv],[S \to a S\bigdot A, b, \dashv, A \dashv], \\
    & [S \to a S A\bigdot , b, \dashv, A \dashv],[S \to b\bigdot , b, \dashv, A \dashv]\}
\end{align*}
The problem is since the production, suffix and prefix is the same as the tuple $[S \to a S A\bigdot , b, \dashv, \dashv]$ the same item set will be created but with a different shortest prefix. The new shortest prefix will always be prepended by $A$ such that $\dashv$ can be derived. This results in this computation can be repeated infinitely. If you compute the next set using $[S \to a S A\bigdot , b, \dashv, A \dashv]$ you will arrive at:
\begin{align*}
    \{& [A \to \bigdot , b, \dashv, A A \dashv],[S \to a S\bigdot A, b, \dashv, A A \dashv], \\
    & [S \to a S A\bigdot , b, \dashv, A A \dashv],[S \to b\bigdot , b, \dashv, A A \dashv]\}
\end{align*}
Therefore the item $[S \to a S\bigdot A, b, \dashv, A^* \dashv]$ will appear infinitely many times in different sets. Algorithm 8 only terminates if a fixed point is reached, but this is impossible, so it will not halt.

This algorithm was not fixed in this paper, instead a grammar is checked for the following. Let $G = (N, T, P, S)$ be a context-free grammar, this grammar may cause an infinite loop if.
\begin{align*}
    \exists \mathcal{N} \in N : \alpha \in (N \cup T)^* \land A \in N \land \mathcal{N} \Rightarrow^* \alpha AA \land A \Rightarrow^* \varepsilon
\end{align*}
This predicate should not capture the essence of the problem. It is intended as a way to make sure not infinitely many nullable nonterminals are prepended to the shortest prefix.

\subsubsection{Determining if a grammar is LLP}
A common answer to whether or not a grammar is a $\LL(k)$ grammar is: if the $\LL(k)$ parser can be constructed, then it is a $\LL(k)$ grammar. The same goes for $\LLP(q,k)$ grammars. That is, a grammar is a $\LLP(q,k)$ if the $\LLP(q, k)$ parser can be constructed.

The first step in determining if a grammar is a $\LLP(q,k)$ grammar is if it is in the $\LL(k)$ grammar class. This is because the LLP parser uses the LL parser to construct the table, therefore the class suffers from the same limitations. The next step is to determine if the $(x, y)$ pair leads to multiple $(\omega, \alpha, \pi)$ LLP configurations. This is what definition 10 \cite[13]{Vagner2007} is used for. To determine if the grammar is LLP.

Definition 10 \cite[13]{Vagner2007} uses the $\PSLS(x, y)$ \cite[12]{Vagner2007} values to determine the initial pushdown stores which can be used to determine the LLP configuration. The trouble when working with LLP grammars the $\PSLS(x, y)$ definition can be troublesome when trying to understand if a grammar is $\LLP(q, k)$. Therefore, some examples of using the definition are given below.

\begin{example}
    \label{ex:llp21}
    Let $(\{A, B\}, \{a, b\}, P, A)$ be a context free grammar where $P$ is.
    \begin{gather*}
        A \to a b b B \qquad B \to b \qquad B \to A
    \end{gather*}
    It will be checked if the grammar is $\LLP(1, 1)$, when computing $\PSLS_1(b,b)$. It can be seen that there exists the following occurrences of $bb$ which leads to two different initial pushdown stores.
    \begin{align*}
        A \Rightarrow_{lm}^* (abb)^*A \Rightarrow (abb)^*abb_xB_{B\gamma} \Rightarrow^* (abb)^*abb_xb_y
    \end{align*}
    This derivation\footnote{The subscripts denote what the symbols correspond to in the $\PSLS$ definition and does change what the symbols mean in the grammar.} corresponds to the first set in the $\PSLS_1(b, b)$ definition. The shortest prefix of $B$ is $B$ where $b \in \FIRST_1(B)$ so $B \in \PSLS_1(b,b)$ \cite[2]{errata:Vagner2007} by definition. The other occurrence comes from the last set in the $\PSLS$ definition.
    \begin{align*}
        A \Rightarrow_{lm}^* (abb)^*A \Rightarrow (abb)^*ab_xb_yB \Rightarrow^* (abb)^*ab_xb_yB
    \end{align*}
    Since $\FIRST_1(b) = \{b\}$ then $b \in \PSLS(b, b)$ by definition. The initial pushdown store for the admissible pair $(b, b)$ is $\PSLS_1(b, b) = \{b, B\}$. Therefore, by Definition 10 \cite[13]{Vagner2007} this grammar is not $\LLP(1, 1)$. If one were to check for all admissible pairs then they would find that $\PSLS_1(b,b)$ is the only problem pair. If one wishes to parse the grammar a $\LLP(2, 1)$ parser can be used. It solves the ambiguities since $\PSLS_1(ab, b) = \{b\}$ and $\PSLS_1(bb, b) = \{B\}$.
\end{example}

\begin{example}
    Let $(\{S\}, \{[, ]\}, P, S)$ be a context free grammar where $P$ is.
    \begin{gather*}
        S \to [S] \qquad S \to \varepsilon
    \end{gather*}
    This grammar seems like it is not $\LLP(q, k)$ for any $q, k \geq 1$. When LL parsing the pairs $([^q, ]^k)$ can lead multiple LL configuration $(]^n, S]^n, \pi)$ where $q + k \leq n$. This grammar is actually a $\LLP(1,1)$ grammar because the LLP parser only uses the shortest prefix of the initial pushdown store in the LLP configuration. This can be determined as not a problem by using the $\PSLS$ definition.
    \begin{align*}
        S \Rightarrow_{lm}^* [^nS]^n \Rightarrow [^{n + 1}S]^{n + 1} \Rightarrow^* [^{n + 1}]^{n + 1}
    \end{align*}
    Here the admissible pair $(x, y)$ are $([^q, ]^k)$ where $q, k \leq n + 1$ for a $\LLP(q, k)$ grammar. Here $B\gamma$ from the definition corresponds to $S]^{n+1}$ and the shortest prefix of $S]^{n+1}$ is $S]^k$. Therefore, this is not a reason for the grammar not being $\LLP(q,k)$.
\end{example}

\begin{example}
    Let $(\{S\}, \{a\}, P, S)$ be a context free grammar where $P$ is.
    \begin{gather*}
        S \to aaS \qquad S \to \varepsilon
    \end{gather*}
    This grammar is mentioned in the LLP paper \cite[16]{Vagner2007} as a grammar that is not $\LLP(q,k)$ for any $q, k \in \mathbb{Z}_+$. This is because the pairs $(a^q, a^k)$, that could lead to the possible initial pushdown stores are $\PSLS_k(a^q, a^k) = \{S, a(S|\epsilon)\}$. This is much the same reason as to why Example \ref{ex:llp21} is not $\LLP(1, 1)$. The trouble with this grammar is even when increasing $q$ or $k$ there is not a symbol that can make $\PSLS_k(a^q, a^k)$ become a singleton. If the productions for the grammar were.
    \begin{gather*}
        S \to aS \qquad S \to \varepsilon
    \end{gather*}
    Then the grammar is $\LLP(1, 1)$ because now only $\PSLS_k(a^q, a^k) = \{S\}$ can occur.
\end{example}